\item The Union Programs and Activities Committee shall be a standing committee of the Executive Board.
\begin{enumerate}

    \item It shall be responsible for organizing events to benefit the entire student body.
    \begin{enumerate}
        \item It shall create such events of its own origin,
        \item It shall provide support for clubs and organizations hosting such events, and
        \item It shall possess and operate resources necessary to make such events possible.
    \end{enumerate}

    \item It shall be the primary operator of Union resources.

    \item It shall establish subcommittees to better maintain and utilize specific facilities and resources with regards to their programming activities.
    \begin{enumerate}
        \item Each subcommittee shall be chaired by a person or persons elected from its membership.
        \item The chair(s) of each subcommittee or his/her duly appointed representatives shall be an officer of the committee.
    \end{enumerate}

    \item It shall establish a standing Grand Marshal Week planning subcommittee responsible for the planning and implementation of all activities that are not directly connected with elections during Grand Marshal Week.

    \item It shall be chaired by a person selected by majority vote of its members and approved by the President and a $\frac{2}{3}$ majority vote of the Executive Board. If the chairpersonship remains vacant and the Committee is unable to select a chair, the President may appoint any member of the Union to the chairpersonship.

\end{enumerate}
