\article{Committees}
\begin{enumerate}

    \item The Chair of each Executive Board Committee, except the Union Programs and Activities Committee, shall be nominated by the President of the Union and confirmed by a $\frac{2}{3}$ majority vote of the Board. Committee Chairs serve at the pleasure of the President. A Vice Chair may be selected by the Chair with the counsel of the President.

    \item Committee membership shall be open to all members of the Rensselaer Union.
    \begin{enumerate}
        \item Any committee member who is not a member of the Executive Board must be approved by the Committee Chair before receiving membership in the committee.
        \item Members of a Committee serve at the pleasure of the Committee Chair and of the President, and may be removed at any time for good cause.
        \begin{enumerate}
            \item Good cause for removal includes, but is not limited to, neglecting the duties of membership, failure to adhere to the rules of order during meetings, or failure to adhere to these bylaws when conducting business in the name of the committee.
            \item Members are expected to dutifully attend meetings of the committee and complete committee assignments within reasonable deadlines.
        \end{enumerate}
    \end{enumerate}
    
    \item During meetings, each Committee shall follow rules of order determined at the discretion of its Chair. Such rules of order shall be made public immediately following their adoption and before any official committee business may commence.

    \item All committees shall be empowered to create subcommittees to aid them in the performance of their functions. The President must be consulted before the creation of any subcommittee. The Committee Chair shall be an ex-officio member of any such subcommittee.

    \item All Committees shall be empowered to set their own policies to aid them in the performance of their functions. These policies may be reviewed and amended by the Executive Board.

    \item Each committee shall meet at least once per month during normal academic period and with enough frequency to satisfy its obligations to the Executive Board.

    \item At the discretion of the President, each Committee Chair shall address the Board at least once per semester to convey the Committee’s activities, projects, and updates.

    \input{Articles/Committees/policies.tex}

    \input{Articles/Committees/business_operations.tex}

    \input{Articles/Committees/map.tex}

    \input{Articles/Committees/upac.tex}

    \item The Executive Board may create Temporary Committees to deal with specific issues as the need arises.
    \begin{enumerate}
        \item These committees shall be given a specific purpose and have such powers granted to it by the Executive Board, to support its given purpose. These powers shall not exceed the powers of the Executive Board.

        \item The Board may impose a time restriction on a Temporary Committee. If no such clause is established by the Board then the Committee shall be disbanded upon the completion of their established goal unless their tenure is extended by a $\frac{2}{3}$ vote of the Board.
    \end{enumerate}

\end{enumerate}
