\article{Meetings}

\begin{enumerate}

    \item The Executive Board shall meet at least once per month during normal academic periods and with enough frequency and regularity to fulfill its duties to the Union.

    \item The time and place of the meetings shall be determined by the President.

    \item Quorum shall consist of $\frac{2}{3}$ of the voting membership of the Executive Board.

    \item All meetings of the Executive Board shall be open to the public. The Executive Board may close a meeting with a $\frac{2}{3}$ vote. The Board can invite non-Board members to a closed meeting with a majority vote. All motions passed during the closed meeting must be made public immediately after the conclusion of the closed meeting. Minutes from a closed portion of a meeting may be released by a $\frac{2}{3}$ vote of the Board.

    \item The Executive Board may vote to open a closed meeting.

    \item The President may remove any person who is disrupting a meeting.
    \begin{enumerate}
        \item The President’s decision may be overruled by the objection of any Representative.
        \item At any time, the President may call for a vote to remove a person from a meeting. This requires a $\frac{2}{3}$ vote of the Board, and if successful can not be overruled.
    \end{enumerate}

    \item Emergency meetings may be called by the President of the Union. In order for any meeting to be considered official and valid, all Board members must be notified of the meeting time and location at least 24 hours before the meeting is scheduled to be held.

    \item At the determination of the President, and with the consent of $\frac{2}{3}$ of all Representatives, the Executive Board may adopt special rules of order for meetings. Written documentation of these special rules of order must exist and be available to all members of the Union. These rules of order shall be subordinate to these Bylaws. In all situations not covered in these bylaws, special rules of order may be used to establish a procedure. In all situations not covered by these special rules of order or by the rules of order described in this document, Robert’s Rules of Order shall be used to answer any questions on procedure.

\end{enumerate}
