\article{Officers}

\begin{enumerate}

    \item The President of the Union is the presiding officer of the Executive Board, hereinafter referred to as the President.

    \item All officers of the Executive Board shall be nominated by the President of the Union and
    confirmed by a $\frac{2}{3}$ vote of the Executive Board.

    \item The President shall nominate a Vice President from the voting membership of the Executive Board. The Vice President shall:
    \begin{enumerate}
        \item Discharge the powers and duties of the President in the cases laid out in Article IX of these Bylaws or at the request of the President.
        \item Oversee the work of all Executive Board Committees.
        \item Coordinate annual documentation of committee work with the committee chairs to ensure continuity between years.
        \item Meet with Committee Chairs once per month to provide an update on committee work.
    \end{enumerate}

    \item The President shall nominate a Secretary of the Executive Board from the Activity Fee paying membership of the Rensselaer Union. It shall be the responsibility of the Secretary to:
    \begin{enumerate}
        \item Record meeting attendance and minutes.
        \item Distribute minutes, committee reports, motions, and other printed material to the members of the Executive Board.
        \item Ensure that minutes, public committee reports, and motions be made public and available to members of the Union no later than one week after the date of such minutes, reports, or motions.
    \end{enumerate}

    \item  The President of the Union shall serve as the Treasurer of the Executive Board.

    \item The President may, at their leisure, appoint other non-voting officers to assist with administering the business of the Executive Board.
    \begin{enumerate}
        \item All non-voting officers of the Executive Board shall serve at the leisure of the President of the Union.
    \end{enumerate}


    \item Officers who are not voting officers of the Executive Board shall regularly attend Executive Board meetings.

\end{enumerate}
