\article{Voting and Debate}

\begin{enumerate}

\item Only Representatives may make motions and vote on any business of the Executive Board. Unless otherwise specified, all votes will be determined by a majority vote.

\item The President may rule any motion out of order. The President’s decision may be overruled by a $\frac{2}{3}$ vote of the Board.

\item Motions that contradict policy or procedure enacted by the Executive Board require at least a $\frac{3}{5}$ majority vote of the Board to pass.

\item The President may vote only in the case of a tie.

\item The following shall be the procedure for all voting unless otherwise specified in special rules of order:
\begin{enumerate}
    \item Voting shall be by a show of hands, unless the President or any Representative requests a roll call.
    \begin{enumerate}
        \item In a show of hands vote, the President will request the number in favor, then the number opposed, then the number of abstentions The President will then announce the result of the vote. In the case of a tie, the President may then announce his/her vote and then the outcome of the vote. The vote count on any motion shall be recorded on the motion and in the minutes by the Secretary and made public with the motion.
        \item If a roll call is requested, the President shall read the names of Representatives ordered alphabetically by surname.
        \begin{enumerate}
            \item Each Representative shall vote or pass, in which case his/her name will be read again after the first completion of the roll call. At this time the Representative must vote or abstain. Refusal to vote shall be determined an abstention.
            \item The result of the roll call shall not be determined until all Representatives present have voted or abstained.
            \item The names of those in favor and those against shall be recorded on the motion and in the minutes by the Secretary and made public with the motion
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\end{enumerate}
